Gut check: site-level analyses

### 2024-09-14 julianna_gut_check.Rmd
Finished gut check code

```{r synchrony summary}
synchrony %>% 
  group_by(habitat, site) %>% 
  summarize(richness_mean_mean = mean(richness_mean), 
            cover_mean_mean = mean(cover_mean), 
            cover_cv_mean = mean(cover_cv), 
            cover_stability_mean = mean(cover_stability), 
            synchrony_trans_mean = mean(synchrony_trans)) -> synchrony_mean
```

```{r alpha summary}
alpha %>% 
  group_by(year, habitat, site) %>% 
  summarize(richness_mean = mean(richness), 
            macroalgal_prop_cover_mean = mean(macroalgal_prop_cover), 
            cover_trans_mean = mean(cover_trans)) -> alpha_mean
```

# Plot synchrony

```{r}
synchrony_mean
```

>>>>

```{r synchrony summary}
synchrony %>% 
  group_by(habitat, site) %>% 
  summarize(richness_mean_mean = mean(richness_mean, na.rm = TRUE), 
            cover_mean_mean = mean(cover_mean, na.rm = TRUE), 
            cover_cv_mean = mean(cover_cv, na.rm = TRUE), 
            cover_stability_mean = mean(cover_stability, na.rm = TRUE), 
            synchrony_trans_mean = mean(synchrony_trans, na.rm = TRUE)) -> synchrony_mean
```

```{r alpha summary}
alpha %>% 
  group_by(year, habitat, site) %>% 
  summarize(richness_mean = mean(richness, na.rm = TRUE), 
            macroalgal_prop_cover_mean = mean(macroalgal_prop_cover, na.rm = TRUE), 
            cover_trans_mean = mean(cover_trans, na.rm = TRUE)) -> alpha_mean
```

# Fig 3

```{r}
synchrony_mean %>% 
  ggplot(aes(x = richness_mean_mean, y = cover_mean_mean, color = habitat, fill = habitat)) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_classic()
```

```{r}
synchrony_mean %>% 
  ggplot(aes(x = synchrony_trans_mean, y = cover_mean_mean, color = habitat, fill = habitat)) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_classic()
```

# Fig 4

Stability on y, richness/synchrony on x

```{r richness}
synchrony_mean %>% 
  ggplot(aes(x = richness_mean_mean, y = 1/cover_cv_mean, color = habitat, fill = habitat)) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_classic()
```

```{r synchrony}
synchrony_mean %>% 
  ggplot(aes(x = synchrony_trans_mean, y = 1/cover_cv_mean, color = habitat, fill = habitat)) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_classic()
```
